A pipeline to analyse time-course gene expression data

### 2020-06-22 scripts/manuscript.Rmd
the data cannot be part of moanin

First let's load the data. The package `moanin` contains the normalized
data and metadata of [@shoemaker:ultrasensitive].

```{r}
# Now load in the metadata
data(shoemaker2015)
meta = shoemaker2015$meta
data = shoemaker2015$data
```

>>>>

First let's load the data. We provide the normalized
data and metadata of [@shoemaker:ultrasensitive] for simplicity.

```{r}
# Now load in the metadata
meta = read.table("../data/shoemaker2015/meta.tsv")
data = read.table(gzfile("../data/shoemaker2015/data.tsv.gz"))
```
